% !TEX program = xelatex

\documentclass{resume}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Pratyush Kar}

\basicInfo{
  \homepage[pratyushkar.com]{https://pratyushkar.com/} \textperiodcentered\ 
  \email{pkar@cs.utexas.edu} \textperiodcentered\ 
  \phone{(+91) 9868826888} \textperiodcentered\ 
  \linkedin[pratyushkar]{https://www.linkedin.com/in/pratyushkar/}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{The University of Texas at Austin}, USA}{2017 -- Present}
\textit{M.S.} in Computer Science
\datedsubsection{\textbf{Birla Institute of Technology \& Science, Pilani}, India}{2013 -- 2017}
\textit{B.E. (Hons.)} in Computer Science \textbf{CGPA: 9.4/10}

\section{\faBriefcase\ Work Experience}
\datedsubsection{\textbf{TEG Analytics}, Bangalore, India}{Jan, 2017 -- May, 2017}
\role{Software Developer Intern}{}
\begin{itemize}
	\item Migrated the Nike team's MS SQL Server setup to a Spark and HDFS based platform.
	\item Implemented the business logics using Spark SQL and columnar storage format (Parquet), resulting in \textasciitilde10x faster query runtimes and \textasciitilde70\% storage savings.
	\item Converted the existing ETL pipeline to the new platform for generating client reports using Tableau dashboards.
\end{itemize}

\datedsubsection{\textbf{Qualcomm India Pvt. Ltd.}, Hyderabad, India}{May, 2016 -- July, 2016}
\role{Software Engineering Intern}{}
\begin{itemize}
	\item Developed a parser and command sequencer (in C++ and Python) for running commands present in the log files to simulate a voice call on the Hexagon DSP simulator.
	\item The system was designed to be dynamic and could handle changes to the ADSP command library seamlessly.
\end{itemize}

\section{\faCodeFork\ Academic Projects}
\datedsubsection{\textbf{Workload Characterisation in Cloud Data Centers}}{Aug, 2016 -- Dec, 2016}
\textit{Advisor: Prof. Sundar B.} \hfill
\begin{itemize}
  \item Developed approaches based on user behavior modeling for the prediction of future workloads on the Google cluster dataset.
  \item Implemented models based on Support Vector Regression for prediction of future CPU and memory usage.
\end{itemize}

\datedsubsection{\textbf{Autonomous Humanoid Robot: AcYut}}{Oct, 2013 -- May, 2016}
\textit{Advisor: Prof. B.K. Rout} \hfill
\begin{itemize}
	\item Designed and built the $6^{th}$ iteration of India's first completely autonomous soccer-playing humanoid robot.
	\item Completed DeitY, Govt. of India, four year funded research project successfully.
	\item Implemented algorithms based on Monte Carlo Localization for efficient localization using field line detection.
	\item Participated and stood $6^{th}$ in RoboCup 2015 (only team from India) held in Hefei, China.
\end{itemize}

\datedsubsection{\textbf{Content Based Image Retrieval for Shekhawati Paintings}}{Jan, 2016 -- May, 2016}
\textit{Advisor: Prof. Sundar B.} \hfill
\begin{itemize}
	\item Implemented graph-based image segmentation algorithms for identifying important objects in the paintings.
	\item Designed image classification algorithms using HOG features and SVM for automatic annotation of the input images in OpenCV.
\end{itemize}

\datedsubsection{\textbf{Multi-Robot Exploration Using TurtleBots}}{Jan, 2015 -- Dec, 2015}
\textit{Advisor: Prof. Sudeept Mohan} \hfill
\begin{itemize}
	\item Designed planning and task allocation algorithms for multiple robots based on Constrained Delaunay Triangulation and successfully tested them on the TurtleBot platform in ROS.
\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Languages: C, C++, Python, Java, Scala, SQL, \LaTeX
  \item Softwares: MATLAB, Tableau, Oracle SQL Developer, IBM SPSS Modeler, Git
  \item Libraries/Frameworks: Apache Spark, Hadoop, OpenCV, pandas, LibSVM, scikit-learn, QT
\end{itemize}

%\section{\faHeartO\ Honors and Awards}
%\datedline{\textit{\nth{1} Prize}, Award on xxx }{Jun. 2013}
%\datedline{Other awards}{2015}
%
%\section{\faInfo\ Miscellaneous}
%\begin{itemize}[parsep=0.5ex]
%  \item Blog: http://your.blog.me
%  \item GitHub: https://github.com/username
%  \item Languages: English - Fluent
%\end{itemize}

\end{document}
