%% TODO: Add Multi Prims details
%% TODO: Add AU details in Kinect
%% TODO: Go through all projects
%% TODO: Mention HiSENS conference
%% TODO: Make AcYut 4 year event
%% TODO: Change publication site links

\documentclass[margin,line]{res}

\usepackage[colorlinks=true, linkcolor=cyan, urlcolor=cyan]{hyperref}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{Pratyush Kar \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2in}p{4in}}
140, Madan Lal Block        & {\it Voice:} (+91) 9868826888 \\            
Asian Games Village         & {\it E-mail:} \href{mailto:pratyush.kar@gmail.com}{pratyush.kar@gmail.com} \\         
New Delhi, India - 110049   & {\it E-mail:} \href{mailto:f20130129@pilani.bits-pilani.ac.in}{f20130129@pilani.bits-pilani.ac.in} \\    
\end{tabular}


%\section{\sc Research Interests}
%Machine Learning, Computer Vision

\section{\sc Education}
{\bf BITS Pilani}, Pilani, Rajasthan, India \hfill {\bf Aug, 2013 -- present}\\
%{\em Department of Computer Science} 
\vspace*{-.1in}
\begin{list1}
\item[] B.E. (Hons.), Computer Science
\begin{list2}
\vspace*{.05in}
\item GPA (10 point): 9.31
\item Major GPA: 9.81
\end{list2}
\vspace*{.05in}
\end{list1}

{\bf The Mother's International School}, New Delhi, India \hfill {\bf 2001 -- 2013}\\
\vspace*{-.1in}
\begin{list1}
\item[] Central Board of Secondary Education (CBSE)
\begin{list2}
\vspace*{.05in}
\item $10^{th}$ GPA (10 point): 9.8
\item $12^{th}$ Percentage: 94.6\%
\end{list2}
\vspace*{.05in}
\end{list1}


%\section{\sc Papers in preparation}
%
%Ventura, V., C.J. Paciorek, and J.S. Risbey.  Controlling the proportion of falsely-rejected hypotheses when conducting multiple tests with geophysical data.
%
%Ickes, K., C.J. Paciorek, and S. Thomas.  Effects of wild pigs on
%forest demographic processes in Malaysia.
%
%\section{\sc Conference Presentations}
%Paciorek, C.J., J.S. Risbey, V. Ventura, and R.D.Rosen.  2001.  Changes in Northern Hemisphere winter storm activity (1949-1999) based
%on a comparison of cyclone indices.  8th International Meeting on
%Statistical Climatology, Luneberg, Germany, March, 2001.
%
%Paciorek, C.J. and R. Rosenfeld.  2000.  Minimum classification error
%training in exponential language models.  2000 Spring Transcription
%Workshop, College Park, Maryland.
%\vspace*{-.25in}  
%\begin{verbatim}http://www.nist.gov/speech/publications/tw00/html/abstract.htm#cp1-50\end{verbatim}

\section{\sc Professional Experience}
{\bf Indian Institute of Remote Sensing (IIRS)}, Dehradun, India

\vspace{-.3cm}
{\em Summer Research Intern} \hfill {\bf 22 May -- 16 July, 2015}\\
\vspace*{-.1in}
\begin{list1}
\item[] Developing a data mining plugin for QGIS (Dr. Sameer Saran)
\begin{list2}
\vspace*{.05in}
\item Designed an open source plugin (in Python) for QGIS to run data mining (like Decision Trees, AdaBoost, and Random Forest) algorithms on multi-band raster datasets.
\end{list2}
\vspace*{.05in}
\item[] Detecting Gradual Change in Noisy Time Series Data (Dr. Shefali Agarwal)
\begin{list2}
\vspace*{.05in}
\item Implemented algorithms for detecting intervals of gradual change in time series vegetation data using persistent delta approach (Chamber et. al).
\end{list2}
\end{list1}

{\bf Qualcomm India Pvt. Ltd.}, Hyderabad, India

\vspace{-.3cm}
{\em Software Engineering Intern} \hfill {\bf 23 May -- 15 July, 2016}\\
Developed a parser and command sequencer (in C++ and Python) for running commands present in the log files to simulate a voice call in ADSP test framework on the Hexagon Simulator.

\section{\sc Academic Projects}

{\bf Content based image retrieval for Shekhawati paintings} (Prof. Sundar B.) \hfill {\bf Spring, 2016}

\vspace*{.2cm}
\begin{list2}
\item Implemented graph-based image segmentation algorithms for identifying important objects in the paintings.
\item Designed image classification algorithms using HOG features and SVM for automatic annotation of the input images.	
\end{list2}

{\bf Hand gesture recognition} (Prof. Navneet Goyal) \hfill {\bf Fall, 2015}

\vspace*{.2cm}
\begin{list2}
\item Implemented classification of multivariate time series gesture data using two-dimensional singular value decomposition (2d-SVD) (Weng et. al).
\item Implemented a real-time hand gesture recognition software using the webcam in MATLAB.	
\end{list2}

{\bf Face expression recognition using Kinect} (Microsoft CodeFunDo) \hfill {\bf Spring, 2016}

\vspace*{.2cm}
\begin{list2}
\item Used Face Tracking SDK to detect the head pose and identify the face features.
\item Used multi-class SVM to create a model to classify the real-time face feature data.
\end{list2}

\begin{minipage}{\linewidth}
{\bf Multi-robot exploration using TurtleBots} (Prof. Sudeept Mohan) \hfill {\bf Jan -- Dec, 2015}

\vspace*{.2cm}
\begin{list2}
\item Designed planning and task allocation algorithms based on Constrained Delaunay Triangulation and tested them on the TurtleBot platform (in ROS).
\end{list2}

\end{minipage}

\begin{minipage}{\linewidth}
{\bf Autonomous humanoid robot: AcYut} (Prof. B.K. Rout) \hfill {\bf Oct, 2013 -- May, 2016}

\vspace*{.2cm}
\begin{list2}
\item Developed a fully autonomous soccer-playing humanoid robot funded by Dept. of Electronics and Information Technology (DeitY, Govt. of India).
\item Implemented algorithms based on Monte Carlo Localization (MCL) for efficient localization using field line detection.
\item Designed the behavior control framework of AcYut 7 (using Extensible Agent Behavior Specification Language, XABSL).
\item Participated and stood $5^{th}$ in RoboCup 2015 (only team from India) held in Hefei, China.
\item Demonstrated AcYut at India-HU workshop for Sensing and Robotics (HiSENS 2015).
\end{list2}

\end{minipage}


\section{\sc Publications}

{\bf Pratyush Kar}, Archit Jain, B.K. Rout. \href{http://dx.doi.org/10.1109/ACIRS.2016.7556191}{Effective localization of humanoid with fish-eye lens using field line detection}. IEEE Asia-Pacific Conference on Intelligent Robot Systems (ACIRS 2016) held in Tokyo, Japan.

Kaustubh Nawade, V. Aditya, {\bf Pratyush Kar}, Anirudh Bhutani, Nishant Bansal, Anant Anurag, Shreyas P. Dixit. \href{https://sites.google.com/site/pratyushkar/publications/Autonomous\%20Humanoid\%20Robot\%20AcYut.pdf?attredirects=0&d=0}{Autonomous humanoid robot AcYut}. Extended abstract accepted at the Developing Countries Forum of the IEEE International Conference on Robotics and Automation (ICRA 2015) held in Seattle, USA.

B.K. Rout, Kaustubh Nawade, V. Aditya, {\bf Pratyush Kar}, Anirudh Bhutani. \href{https://sites.google.com/site/pratyushkar/publications/Team\%20AcYut\%20\%E2\%80\%93\%20Team\%20Description\%20Paper\%202015.pdf?attredirects=0&d=0}{Team AcYut -- Team Description Paper 2015}. RoboCup 2015 Symposium held in Hefei, China.

{\bf Pratyush Kar}, Sameer Saran. \href{https://sites.google.com/site/pratyushkar/publications/SpatialDM.pdf?attredirects=0&d=0}{SpatialDM: An open source data mining plugin for QGIS}. Journal of Geomatics, Vol. 9 No. 2, pp. 141-145, 2015.

\section{\sc Teaching Experience}
{\bf BITS Pilani}, Pilani, Rajasthan, India

\vspace{-.3cm}
{\em Teaching Assistant} \hfill {\bf Spring, 2016}\\
Co-taught an undergraduate course to over 200 students.  Shared responsibility for labs, programming assignments, and grades.
\vspace*{.05in}  
\begin{list2}
\item CS F211 Data Structures and Algorithms
\end{list2}


\section{\sc Honors and Awards}

Awarded merit scholarship by BITS Pilani, for exceptional academic performance.

\vspace*{-2.5mm}
Recipient of Kishore Vaigyanik Protsahan Yojana (KVPY) scholarship, awarded by the Department of Science and Technology (Govt. of India), 2013.


\section{\sc Computer Skills} 
\begin{list2}
\item Softwares: MATLAB, IBM SPSS Modeler, Oracle SQL Developer, Git
\item Languages:  C, C++, Python, Java, SQL, Prolog, \LaTeX
\item Libraries: XABSL, OpenCV, QT, cvBlob, LibSVM
\item Operating Systems:  Unix/Linux, Mac OS, Windows\\ 
\end{list2}


\section{\sc Extra Curriculars}

{\bf Photography}

\vspace*{.2cm}
\begin{list2}
\item Completed a diploma course on DSLR photography under Mr. Nitin Rai.
\end{list2}

\section{\sc Languages}

English, Hindi (native).



\end{resume}
\end{document}




